The PFA was implemented within the RISC-V ecosystem. RISC-V is an open-source
instruction set with several open and closed-source implementations and ports
for many common software components\cite{riscv}.

% \subsection{PFA Reference Implementation}
% To accelerate software development, and to provide a golden-model of
% PFA behavior, we implemented the PFA first in a RISC-V ISA simulator called
% "Spike"\cite{spike}. Spike provides a functional simulation of a RISC-V core
% through a straightforward C++ interpreter, but does not provide any timing
% accuracy. Due to its simplicity, the PFA implementation required only a few
% weeks of implementation effort and less than 1000 LoC. With Spike, software
% development was able to proceed concurrently with the concrete hardware design.
% Furthermore, unit tests developed under Spike were used to validate the
% hardware implementation, reducing debugging effort. In all, the only software
% change that was needed to go from Spike to a concrete implementation was one
% extra TLB flush due to a difference in TLB design between Spike and the RISC-V
% implementation we used.
%
\subsection{Hardware Implementation}
The PFA prototype was implemented in the Chisel hardware construction
language\cite{chisel} and integrated with a simple in-order CPU called
RocketCore\cite{rocketchip}. The components were integrated using the
RocketChip system-on-chip (SoC) generator\cite{rocketchip}. We provide an
overview of the relevant systems in the following sections. The current PFA
prototype implements a subset of the specification described in Section
\ref{sec:pfaDesign}. Specifically, it does not support multiple simultaneous
evictions (the EvictQ has an effective depth of 1), however, it does allow for
asynchronous eviction. This prevents optimizations such as switching to other
threads while many pages are simultaneously evicted (a single eviction does not
take long enough to justify a context switch). 

\subsubsection{RocketCore and RocketChip}
RocketChip\cite{rocketchip} is a framework for generating SoCs. It includes
on-chip interconnects, caches, and other utilities for chip construction. While
the CPU is pluggable, we use only a single RocketCore in-order CPU for our
experiments. Our implementation used dedicated 16KB instruction and data
caches \todo{Details of rocket target}. While the node had access to several gigabytes of main memory, we
artificially limited application memory using Linux cgroups (see Section
\ref{sec:eval} for details). A real \gls{wsc} would likely include a mixture of
simple cores, high single-thread performance cores, and
accelerators. We hope to evaluate the Berkeley out-of-order core
(BOOM\cite{BOOM}) and the Hwatcha vector accelerator\cite{hwatcha} in the
future when they become available in our simulation infrastructure.

\subsubsection{FireSim}
We simulated the RTL using a cycle-accurate simulator called
"FireSim"\cite{firesim}. FireSim is an FPGA-accelerated simulator that runs on
the Amazon cloud. It can simulate thousands of nodes with a cycle-accurate
network and heterogeneous components. Many parameters of the simulation are
tunable within FireSim. We decided on a \SI{200}{\giga\bit\per\second} network
with \SI{500}{\nano\second} link latency, leading to roughly 2us page access
time to the memory blade (similar to current infiniband networks).

\begin{figure}[h]
\centering
\begin{tabular}{| l | l |}
  \hline
  \textbf{CPU Type} & Rocket (5-stage in order) \\ \hline
  \textbf{CPU Frequency} & \SI{3.2}{\giga\hertz} \\ \hline
  \textbf{Caches} & \SI{16}{\kilo\byte} D\$ and I\$ \\ \hline
  \textbf{NW Topology} & Single Switch \\ \hline
  \textbf{NW Bandwidth} & \SI{200}{\giga\bit\per\second} \\ \hline
  \textbf{NW Link Latency} & \SI{2}{\micro\second} \\ \hline
  \textbf{Remote Page Read} & \SI{4.8}{\micro\second} \\ \hline
  \textbf{Remote Page Write} & \SI{4.8}{\micro\second} \\ \hline
\end{tabular}
\caption{System parameters used for evaluation.}
\label{tbl:sim_parameters}
\end{figure}

\subsection{Linux Integration} \label{sec:linuxImpl}
    \input{tex/linuxDesign.tex}
